GRASS GIS image processing environment\\ Gearing towards GRASS GIS 7

### 2013-03-19 grassposter/2013_EGU_G7_Landscape/poster.tex
unmix images replaced with high-res PDF version
git-svn-id: https://svn.osgeo.org/grass/grass-promo@55435 15284696-431f-4ddb-bdfa-cd5b030d7da7
Remove Bold on paragraph
git-svn-id: https://svn.osgeo.org/grass/grass-promo@55436 15284696-431f-4ddb-bdfa-cd5b030d7da7

\startfourthcolumn
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Multi- and hyperspectral data analysis}{
\smallskip
{\bf Unmixing mixed pixels (i.spec.unmix [9]) is based upon identifying orignal spectral signatures
that ideally come from a land cover that is covering at least one full pixel in the image
studied.}

\begin{center}
 \includegraphics[width=0.4\textwidth]{./images/unmix1.png}
 \hspace{10mm}
 \includegraphics[width=0.5\textwidth]{./images/unmix.png}
\end{center}
\begin{center}
 \includegraphics[width=0.5\textwidth]{./images/unmix2.png}
 \newline
 Figure 7: Unmixing principle (left), end-members selection (right), error space (below)
\end{center}
}

>>>>

\startfourthcolumn
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Multi- and hyperspectral data analysis}{
\smallskip
Unmixing mixed pixels (i.spec.unmix [9]) is based upon identifying orignal spectral signatures
that ideally come from a land cover that is covering at least one full pixel in the image
studied.

\begin{center}
 \includegraphics[width=0.4\textwidth]{./images/unmix_pixels_spectrum.pdf}
 \hspace{10mm}
 \includegraphics[width=0.5\textwidth]{./images/unmix_xgobi_supersession.pdf}
\end{center}
\begin{center}
 \includegraphics[width=0.5\textwidth]{./images/unmix_errorfunction.pdf}
 \newline
 Figure 7: Unmixing principle (left), end-members selection (right), error space (below)
\end{center}
}
